---
knit: (function(input, ...) {
    juicedown::convert(file = input, clip = FALSE)
  })
---

# Notes

```{r setup, include = FALSE}
library(juicedown)
```

This app provides an interface for R package [juicedown](https://CRAN.R-project.org/package=juicedown). If you require full control, please use [juicedown](https://CRAN.R-project.org/package=juicedown) directly.

The version of the app hosted on Shinyapps.io has further restrictions on executing arbitrary R code due to security reasons. This limitation is in place to prevent the risk of users running malicious code. If you prefer the user-friendly interface, run [juicedownApp](https://github.com/kenjisato/juicedownApp) locally. See the installation section below.

In restricted mode, you still have access to a few app-only commands.

## Special Commands

### YouTube Video

```markdown
{% YouTube("https://youtu.be/videoid") %}
```

```{r, results='asis', echo=FALSE}
includeYT("https://youtu.be/L1Sks-inb9M")
```



### Audio File

```markdown
{% Audio("https://example.com") %}
```

```{r}
includeAudio("https://omunet-my.sharepoint.com/:u:/g/personal/s21413e_omu_ac_jp/EcPrgs7iZKNAm8yGWK_vGE0BEc_gfAfUToP1i7wTe01vSA?e=ajLbXP&download=1")
```


## Install juicedown and juicedownApp

To install:

```r
install.packages("remotes")
remotes::install_github("kenjisato/juicedownApp")
```

To run the app on the local server: 

```r
juicedownApp::up()
```


